\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 draft.tex
Modification of teh first paragraph of 4.2

After the transformation described above, the reducer $s_1;\rloop\{s_2\};s_3$
never calls the $\cur$ function in the $s_1$ part before entering the loop. W.o.l.g, we assume that the reducer reads exactly one input in one loop iteration.
For the case that multiple reads from input occur in the loop, we can break the multiple reads to several single reads over multiple loop iterations using auxiliary variables and branch statements.

@@

J-ReCoVer successfully handled $115$ cases ($97.5~\%$) out of the considered
ones. The analysis time ranged between $9.8$ and $8.6$ seconds. On average,
$72~\%$ of the execution time was spent in compiling Java source code to
bytecode, which is the input of the Soot tool. Further, $27~\%$ of the execution
time was spent in the Preprocessor, in which Soot is used to transform Java
bytecode to Jimple and perform the program transformation. The time spent in
Solver is quite limited ($<1~\%$) since the real-world integer reducer programs
are usually not that big.

>>>>

After the transformation described above, the reducer $s_1;\rloop\{s_2\};s_3$
never calls the $\cur$ function in the $s_1$ part before entering the loop.
Further, we assume w.l.o.g. that the reducer reads exactly one input in one loop
iteration. When multiple reads from the input occur in a single branch of the
loop, we can use additional variables and break the branch into several
auxiliary ones, each reading just once.

@@

J-ReCoVer successfully handled $115$ cases ($97.5~\%$) out of the considered
ones. Among them, $106$ cases are commutative, while $9$ are not. The analysis time ranged between $9.8$ and $8.6$ seconds. On average,
$72~\%$ of the execution time was spent in compiling Java source code to
bytecode, which is the input of the Soot tool. Further, $27~\%$ of the execution
time was spent in the Preprocessor, in which Soot is used to transform Java
bytecode to Jimple and perform the program transformation. The time spent in
Solver is quite limited ($<1~\%$) since the real-world integer reducer programs
are usually not that big.
